Supporting Non-Functional Requirements for Services Software Process: An MDD Approach

### 2013-10-19 SOFSEM2014/FinalVersion/introduction.tex
minor changes everywere -- Martin

Model Driven Development (MDD) is top-down approach for the design and development of software systems. 
The main ideas of MDD were originaly proposed by the Object Management Group
(OMG)~\cite{mda}. 
MDD provides a set of
guidelines for the structuring of specifications.
The technique advocates for the use of \textit{models} to specify a software system at different levels of abstraction.
Abstraction levels are called \textit{viewpoints}. 
MDD defines three viewpoints:

>>>>

Model Driven Development (MDD)~\cite{Favre06arigorous} is a top-down approach for the design and development of software systems. 
The main ideas of MDD were originaly proposed by the Object Management Group
(OMG)\footnote{\texttt{http://www.omg.org/mda}.}. 
MDD provides a set of
guidelines for the structuring of specifications.
The technique advocates for the use of \textit{models} to specify a software system at different levels of abstraction.
Abstraction levels are called \textit{viewpoints}. 
MDD defines three viewpoints:
